Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-23 manuscript/manuscript.Rmd
nicer figure

```{r state-space}
i_tac <- which.min(abs(actions - best_action * 0.8))

# color pallette limits
library(RColorBrewer)
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(0,1))

pmsy <- msy |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == best_action) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  theme(aspect.ratio = 1/1)

ptac <- msy |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == actions[[i_tac]]) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  theme(aspect.ratio = 1/1)

pppo <- ppo |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  theme(aspect.ratio = 1/1)

pesc <- opt_escapement |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, 
        harvest = case_when(
          X - esc_level > 0 ~ X - esc_level,
          X - esc_level <= 0 ~  0)
         ) |> 
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  theme(aspect.ratio = 1/1)

>>>>

```{r state-space, fig.cap="TBD.", out.width = "6.5in"}
i_tac <- which.min(abs(actions - best_action * 0.8))

# color pallette limits
library(RColorBrewer)
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(0,0.25))

pmsy <- msy |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == best_action) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("Opt. Const. Mortality")

ptac <- msy |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == actions[[i_tac]]) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("80% Opt. Const. Mortality")

pppo <- ppo |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("DRL")

pesc <- opt_escapement |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, 
        harvest = case_when(
          X - esc_level > 0 ~ X - esc_level,
          X - esc_level <= 0 ~  0)
         ) |> 
  ggplot(aes(X, Z, color = harvest)) +
  geom_point() + sc +
  ggtitle("Opt. Const. Escapement")
